---
title: "AIGRA Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AIGRA Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = '#>'
)
```

# Overview

AIGRA stands for **Agentic Item Generation, Review, and Analysis**.

The package provides tools for working with assessment item generation workflows, including item-bank templates, validation, Python-backed generation workflows, multimodal diagram generation, quality summaries, and HTML reports.

External artificial intelligence services require user-supplied API keys and are not called in this vignette.

# Load AIGRA

```{r}
library(AIGRA)
```

# Create an item-bank template

```{r}
template <- aigra_template_items()
template
```

# Validate a bundled example item bank

```{r}
example_path <- aigra_example_item_bank()
validation <- aigra_validate_tabular_items(example_path)
aigra_print_validation(validation)
```

# Supported image models

```{r}
aigra_image_models()
```

# Backend configuration

The full AIGRA generation workflow uses an optional Python backend.

```{r, eval = FALSE}
Sys.setenv(AIGRA_BACKEND_PATH = 'path/to/AIGRA_BACKEND')
aigra_set_backend()
aigra_status()
```

# AI-assisted generation

Generation functions require an installed backend and user-supplied API keys. They are shown here but not evaluated during package checks.

```{r, eval = FALSE}
Sys.setenv(GEMINI_API_KEY = 'your_gemini_key')

result <- aigra_generate_tabular_items(
  file_path = example_path,
  provider = 'gemini',
  model = 'gemini-3.1-pro-preview',
  source_language = 'English',
  target_language = 'English',
  subject = 'Physics',
  exam = 'Demo Item Bank',
  n_clones = 1,
  max_items = 1
)
```

# Diagram generation

```{r, eval = FALSE}
result2 <- aigra_generate_result_diagrams(
  result,
  provider = 'gemini',
  model = 'gemini-3-pro-image-preview',
  only_required = FALSE,
  force = TRUE,
  max_images = 1
)

aigra_show_result_diagram(result2, 1)
```

# Reporting

```{r, eval = FALSE}
aigra_print_summary(result)
aigra_plot_summary(result)
report_path <- aigra_write_report(result)
browseURL(report_path)
```
